---
title: "Which Web Map Services Work in Web Maps?"
author: Adam Sisco and Kane Cook
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(leaflet)
```

> W3C's [Spatial Data on the Web Best Practices](https://www.w3.org/TR/sdw-bp/) states that geospatial data (i.e., data about things located relative to the Earth) should, at a minimum, be provided in a global coordinate reference system; for raster data, this should be Web Mercator (EPSG:3857).

## {.tabset .tabset-fade}

### NASA

#### NASA EOSDIS GIBS
[GetCapabilities](https://gibs.earthdata.nasa.gov/wms/epsg3857/best/wms.cgi?SERVICE=WMS&REQUEST=GetCapabilities&VERSION=1.3.0)  
Layer name: `MODIS_Terra_CorrectedReflectance_TrueColor`  
Notes: Service supports EPSG:3857
```{r gibs}
leaflet(width = "100%", height = "350px") %>% addTiles() %>% setView(lng = -70, lat = 30, zoom = 3) %>%
  addWMSTiles(
    "https://gibs.earthdata.nasa.gov/wms/epsg3857/best/wms.cgi",
    layers = "MODIS_Terra_CorrectedReflectance_TrueColor",
    options = WMSTileOptions(format = "image/png", transparent = TRUE, time = "2018-01-04"))
```

---

#### SEDAC
[GetCapabilities](https://sedac.ciesin.columbia.edu/geoserver/ows?service=WMS&version=1.3.0&request=GetCapabilities)  
Layer name: `gpw-v4:gpw-v4-population-density-adjusted-to-2015-unwpp-country-totals_2020`  
Notes: Service supports EPSG:3857
```{r sedac}
leaflet(width = "100%", height = "350px") %>% addTiles() %>% setView(lng = 80, lat = 20, zoom = 3) %>%
  addWMSTiles(
    "https://sedac.ciesin.columbia.edu/geoserver/ows",
    layers = "gpw-v4:gpw-v4-population-density-adjusted-to-2015-unwpp-country-totals_2020",
    options = WMSTileOptions(format = "image/png", transparent = TRUE, opacity = 0.5))
```

---

#### NASA NEO <span style="color:red">(Does not render; lacks EPSG:3857 support)</span>
[GetCapabilities](https://neo.sci.gsfc.nasa.gov/wms/wms?version=1.3.0&service=WMS&request=GetCapabilities)  
Layer name: `MYD28M`  
Notes: No support for EPSG:3857
```{r neo}
leaflet(width = "100%", height = "350px") %>% addTiles() %>% setView(lng = 0, lat = 20, zoom = 2) %>%
  addWMSTiles(
    "https://neo.sci.gsfc.nasa.gov/wms/wms",
    layers = "MYD28M",
    options = WMSTileOptions(format = "image/png", transparent = TRUE))
```

---

#### GES DISC AIRS
[GetCapabilities](https://disc1.gesdisc.eosdis.nasa.gov/daac-bin/wms_airs?service=WMS&version=1.3.0&request=GetCapabilities)  
Layer name: `AIRX3STM_TOTH2OVAP_A`  
Notes: Service supports EPSG:3857
```{r airs}
leaflet(width = "100%", height = "350px") %>% addTiles() %>% setView(lng = 0, lat = 20, zoom = 2) %>%
  addWMSTiles(
    "https://disc1.gesdisc.eosdis.nasa.gov/daac-bin/wms_airs",
    layers = "AIRX3STM_TOTH2OVAP_A",
    options = WMSTileOptions(format = "image/png", transparent = TRUE, opacity = 0.4))
```

---

#### ORNL DAAC <span style="color:red">(Scattered support for EPSG:3857)</span>
[GetCapabilities](https://webmap.ornl.gov/ogcbroker/wms?&service=WMS&version=1.1.1&request=GetCapabilities)  
Layer name: `1345_113` (served in EPSG:3857) and `1343_38` (lacks EPSG:3857)  
Notes: Service has scattered support for EPSG:3857
```{r ornl}
leaflet(width = "100%", height = "350px") %>% addTiles() %>% setView(lng = -88, lat = 33, zoom = 5) %>%
  addWMSTiles(
    "https://webmap.ornl.gov/ogcbroker/wms",
    layers = "1343_38",
    options = WMSTileOptions(format = "image/png", transparent = TRUE, opacity = 0.4), group = "1343_38 (lacks EPSG:3857)") %>%
  addWMSTiles(
    "https://webmap.ornl.gov/ogcbroker/wms",
    layers = "1345_113",
    options = WMSTileOptions(format = "image/png", transparent = TRUE, opacity = 0.4), group = "1345_113 (served in EPSG:3857)") %>%
   addLayersControl(
    overlayGroups = c("1343_38 (lacks EPSG:3857)", "1345_113 (served in EPSG:3857)"),
    options = layersControlOptions(collapsed = FALSE))
```

---

#### GES DISC OMI <span style="color:red">(Does not render; lacks EPSG:3857 support)</span>
[GetCapabilities](https://disc1.gesdisc.eosdis.nasa.gov/daac-bin/wms_omi?service=WMS&version=1.3.0&request=GetCapabilities)  
Layer name: `OMTO3d_Column_Amount_O3`  
Notes: No support for EPSG:3857
```{r omi}
leaflet(width = "100%", height = "350px") %>% addTiles() %>% setView(lng = 0, lat = 20, zoom = 2) %>%
  addWMSTiles(
    "https://disc1.gesdisc.eosdis.nasa.gov/daac-bin/wms_omi",
    layers = "OMTO3d_Column_Amount_O3",
    options = WMSTileOptions(format = "image/png", transparent = TRUE))
```

---

#### GES DISC NRT AIRS <span style="color:red">(Does not render; lacks EPSG:3857 support)</span>
[GetCapabilities](https://disc1.gesdisc.eosdis.nasa.gov/daac-bin/wms_airsnrt?service=WMS&version=1.3.0&request=GetCapabilities)  
Layer name: `AIRS_RH850_A`  
Notes: No support for EPSG:3857
```{r airsNRT}
leaflet(width = "100%", height = "350px") %>% addTiles() %>% setView(lng = 0, lat = 20, zoom = 2) %>%
  addWMSTiles(
    "https://disc1.gesdisc.eosdis.nasa.gov/daac-bin/wms_airsnrt",
    layers = "AIRS_RH850_A",
    options = WMSTileOptions(format = "image/png", transparent = TRUE))
```

---

#### PO.DAAC THREDDS WMS
[GetCapabilities](https://thredds.jpl.nasa.gov/thredds/wms/ncml_aggregation/OceanTemperature/modis/terra/11um/4km/aggregate__MODIS_TERRA_L3_SST_THERMAL_MONTHLY_4KM_DAYTIME_V2014.0.ncml?service=WMS&version=1.3.0&request=GetCapabilities)  
Layer name: `sst`  
Notes: Service supports EPSG:3857
```{r podaac}
leaflet(width = "100%", height = "350px") %>% addTiles() %>% setView(lng = 0, lat = 20, zoom = 2) %>%
  addWMSTiles(
    "https://thredds.jpl.nasa.gov/thredds/wms/ncml_aggregation/OceanTemperature/modis/terra/11um/4km/aggregate__MODIS_TERRA_L3_SST_THERMAL_MONTHLY_4KM_DAYTIME_V2014.0.ncml",
    layers = "sst",
    options = WMSTileOptions(format = "image/png", transparent = TRUE))
```

---

#### NASA FIRMS
[GetCapabilities](https://firms.modaps.eosdis.nasa.gov/wms/?SERVICE=WMS&VERSION=1.1.1&REQUEST=GETCAPABILITIES)  
Layer name: `fires_modis_24`  
Notes: Service supports EPSG:3857
```{r firms}
firms_key <- readLines("firms-map-key.txt")

leaflet(width = "100%", height = "350px") %>% addTiles() %>% setView(lng = 0, lat = 20, zoom = 2) %>%
  addWMSTiles(
    "https://firms.modaps.eosdis.nasa.gov/wms/",
    layers = "fires_modis_24",
    options = WMSTileOptions(format = "image/png", transparent = TRUE, map_key=firms_key))
```

### Other

#### NLCD
[GetCapabilities](https://www.mrlc.gov/geoserver/mrlc_display/NLCD_2016_Land_Cover_L48/wms?service=WMS&request=GetCapabilities)  
Layer name: `NLCD_2016_Land_Cover_L48`  
Notes: Service supports EPSG:3857
```{r nlcd}
leaflet(width = "100%", height = "350px") %>% addTiles() %>% setView(lng = -99, lat = 38.5, zoom = 4) %>%
  addWMSTiles(
    "https://www.mrlc.gov/geoserver/mrlc_display/NLCD_2016_Land_Cover_L48/wms",
    layers = "NLCD_2016_Land_Cover_L48",
    options = WMSTileOptions(format = "image/png", transparent = TRUE))
```

---

#### U.S Drought Monitor
[GetCapabilities](http://ndmc-001.unl.edu:8080/cgi-bin/mapserv.exe?map=/ms4w/apps/usdm/service/usdm_20120821_wms.map&SERVICE=WMS&VERSION=1.3.0&REQUEST=GetCapabilities)  
Layer name: `usdm20120821`  
Notes: Service supports EPSG:3857
```{r drought}
leaflet(width = "100%", height = "350px") %>% addTiles() %>% setView(lng = -99, lat = 38.5, zoom = 4) %>%
  addWMSTiles(
    "http://ndmc-001.unl.edu:8080/cgi-bin/mapserv.exe?map=/ms4w/apps/usdm/service/usdm_20120821_wms.map",
    layers = "usdm20120821",
    options = WMSTileOptions(format = "image/png", transparent = TRUE, opacity = 0.5))
```

---

#### NOAA nowCOAST
[GetCapabilities](https://nowcoast.noaa.gov/arcgis/services/nowcoast/analysis_meteohydro_sfc_qpe_time/MapServer/WMSServer?request=GetCapabilities&service=WMS)  
Layer name: `9`  
Notes: Service supports EPSG:3857
```{r nowcoast}
leaflet(width = "100%", height = "350px") %>% addTiles() %>% setView(lng = -99, lat = 38.5, zoom = 4) %>%
  addWMSTiles(
    "https://nowcoast.noaa.gov/arcgis/services/nowcoast/analysis_meteohydro_sfc_qpe_time/MapServer/WMSServer",
    layers = "9",
    options = WMSTileOptions(format = "image/png", transparent = TRUE, opacity = 0.5))
```

---

#### U.S Fish and Wildlife Service
[GetCapabilities](https://www.fws.gov/wetlands/arcgis/services/Wetlands_Raster/ImageServer/WMSServer?request=GetCapabilities&service=WMS)  
Layer name: `0`  
Notes: Service supports EPSG:3857
```{r wetlands}
leaflet(width = "100%", height = "350px") %>% addTiles() %>% setView(lng = -90, lat = 30, zoom = 6) %>%
  addWMSTiles(
    "https://www.fws.gov/wetlands/arcgis/services/Wetlands_Raster/ImageServer/WMSServer",
    layers = "0",
    options = WMSTileOptions(format = "image/png", transparent = TRUE, opacity = 0.75))
```
